\begin{thebibliography}{90}             %crea l'ambiente bibliografia
\rhead[\fancyplain{}{\bfseries
BIBLIOGRAFIA}]{\fancyplain{}{\bfseries\thepage}}
\lhead[\fancyplain{}{\bfseries\thepage}]{\fancyplain{}{\bfseries
BIBLIOGRAFIA}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%aggiunge la voce Bibliografia
                                        %   nell'indice
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{K1} S. Nakamoto, “Bitcoin: A Peer-to-Peer Electronic Cash System,” p. 9.
\bibitem{K2} A. M. Antonopoulos (2017, June). Mastering Bitcoin, Programming the open blockchain. O'Reilly Media.
\bibitem{K3} OECD, OECD Blockchain Primer.
\bibitem{K4} Consensys Academy. Blockchain Basics Book.
\bibitem{K5} District0x Education Portal, What Is An ERC20 Token?
\bibitem{K6} ERC721 Standard (2018) http://erc721.org/
\bibitem{K7} Consensys Web3Studio. Bootleg, A Community for Royalty Sharing. https://consensys.net/web3studio/bootleg.
\bibitem{K8} A. B. Bondi (2000), Characteristics of Scalability and Their Impact on Performance.
\bibitem{K9} L. Lamport (1978), Time, Clocks, and the Ordering of Events in a Distributed System.
\bibitem{K10} F. C{\"a}sar, D. P. Hughes, J. Primero, S. J. Thornton, Cerberus, A Parallelized BFT Consensus Protocol for Radix, v1.0 (2020, March).
\bibitem{K11} G. Minello (2019), Metodologie per la realizzazione di una Security Token Offering.
\bibitem{K12} Sophie Donkin (2020, February), Dan And Radix's Tech Journey. Radix DLT Blog. https://www.radixdlt.com/post/dan-and-radixs-tech-journey/
\bibitem{K13} Matthew Hine (2019, November), Radix Engine and Ledger: The Road to Adoption. Radix DLT Blog. https://www.radixdlt.com/post/radix-engine-and-ledger-the-road-to-adoption/
\bibitem{K14} Carlotta Balena, Liberi dagli intermediari. Fortune Italia n. 5, Maggio 2019, p. 60.
\bibitem{K15} Bootleg, Wikipedia.  https://it.wikipedia.org/wiki/Bootleg
\bibitem{K16} Ethereum GitHub Wiki (2019, April) Sharding FAQ.
\bibitem{K17} Trent McConaghy (2016), The DCS Triangle: Decentralized, Consistent, Scalable. Pick any two. Medium.
\bibitem{K18} The Radix Basics (2018) https://www.radixdlt.com/post/the-radix-basics/
\bibitem{K19} Radix Engine: A Simple, Secure Smart Contract Alternative (2019). https://www.radixdlt.com/post/radix-engine-a-simple-secure-smart-contract-alternative/
\bibitem{K20} Why we are open sourcing (2020). https://www.radixdlt.com/post/why-we-are-open-sourcing/
\bibitem{K21} Consensys Academy (2018, January), Ethereum Limitations and scaling solutions.
\bibitem{K22} Buterin, V. (2013). Ethereum white paper. GitHub repository
\bibitem{K23} Matthew Hine (2019) Radix Engine and Ledger, The road to adoption. Radix DLT Blog
\bibitem{K24} Radix Engine Library. radixdlt GitHub repository
\bibitem{K25} Axios Github Repository https://github.com/axios/axios
\bibitem{K26} https://radixdlt.github.io/library-api-docs/radixdlt-js/2.0.0-beta.1/
\bibitem{K27} https://docs.radixdlt.com/radixdlt-js/examples/code-examples
\bibitem{K28} https://github.com/radixdlt/radixdlt-js-showcase
\bibitem{K29} https://docs.radixdlt.com/kb/develop/betanet-emulator
\bibitem{K30} https://ipfs.io/

\end{thebibliography}